\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
Minor modifications in the evaluation

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \vspace{-20pt}
    \caption{
      \textbf{\sys's speedup for \ttiny{width=}2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
}
    \vspace{-14pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

Plots do not include lines for configurations that lead to identical parallel programs.
There are two types of such cases. %  (that appear in \todo{five} plots).
In the first, the \emph{Pash} (blue) and \emph{Pash-w/o-split} (red, hidden) lines are identical for scripts that \sys does not add \ttt{split} since the width of the DFG is constant;
%  when \sys adds no \ttt{split} because the DFG width remains constant for the whole program;
  conversely, when both lines are shown (\eg Spell, Bi-grams, and Sort), \sys has added \ttt{split}s due to changes in the DFG width (e.g. due to a \npu command).
In the second type, \emph{Pash w/o Split} (red) is identical to \emph{No-Eager} (green, hidden) and \emph{Blocking Eager} (orange, hidden) because the input script features a command in \pur or \npu relatively early.
This command requires an \ttt{agg}regator, whose output is of width 1, and beyond which non-\ttt{split} configurations are sequential (and see no speedup).
% Conversely, all three lines exist when the width remains above 1 for the full program.
% needing a \ttt{split} to regain width.

Finally, Tab.~\ref{tab:eval} shows that \sys's transformation time is negligible, and its COST~\cite{mcsherryscalability} is 2. %  for all benchmarks.
% Filter and Bigrams-opt, not in Fig.~\ref{fig:microbenchmarks}, achieve speedups of 1.5--2.5$\times$ and 2--30$\times$.
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

@@

\heading{Results}
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for 31 pipelines, with \ttt{width=}16 and 10GB inputs.
It does not include 3 pipelines that execute in under $0.1s$ by using \ttt{head} to output the first line of input.
The script index refers to the challenge level, in both the plots and the discussion.
Average speedup is \todo{$6.02\times$}, % median is $6.48\times$, 
  and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

%% \kk{Out of all benchmarks, we have talked about the head and the
%%   non-parallelizable ones in the paper. Maybe we also want to talk
%%   about the long and the cheap ones. Also we might want to talk and
%%   find out more about the sort bottleneck.}

%% (OLD) Bad result descriptions:
%%  2. Contains just a head -n 2, and then a cut.
%%  5. Very fast (small input). Sequential time is 0m0.103s (If we increase the input we will show speedup)
%%  18. TODO: Implement
%%  20. Four corners (not parallelizable). So performance is reasonable
%%      (atm it doesn't return the correct result for multiplied input though)
%%  21. Last capital character of each line. Their solution is not general (and it is not parallelizable).
%%      Also, the input is very small. Changing it to a more general one and
%%      increasing input size leads to speedup. TODO: Run with large input
%%  22. Exactly the same problem as the above.
%%  24. (Not sure: It seems that the computation is trivial)
%%  32. TODO: Implement

\heading{Take-aways} \sys accelerates unmodified pipelines found in the wild;
  small tweaks can yield further improvements, showing that \sys-awareness and scripting expertise can improve results.
Furthermore, \sys does not decelerate non-trivial computations, even when parallelism is impossible.

@@

\heading{Results}
The complete pipeline executes in 44m2s for five years (82GB) of data.
\sys with \ttt{width=}16 leads to \todo{2.44$\times$} speedup, with different phases seeing different benefits:
  \todo{1.99$\times$} (vs. 33m58s) for all the pre-processing and 
  \todo{10.79$\times$} speedup (vs. 10m4s) for computing the max.

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \vspace{-20pt}
    \caption{
      \textbf{\sys's speedup for \ttiny{width=}2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
  % \kk{FUTURE: Run and show all plots (with and without split for all experiments.)}
}
    \vspace{-14pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

Plots do not include lines for configurations that lead to identical parallel programs.
There are two types of such cases. %  (that appear in \todo{five} plots).
In the first, the \emph{Pash} (blue) and \emph{Pash-w/o-split} (red, hidden) lines are identical for scripts that \sys does not add \ttt{split} since the width of the DFG is constant;
%  when \sys adds no \ttt{split} because the DFG width remains constant for the whole program;
  conversely, when both lines are shown (\eg Spell, Bi-grams, and Sort), \sys has added \ttt{split}s due to changes in the DFG width (e.g. due to a \npu command).
In the second type, \emph{Pash w/o Split} (red) is identical to \emph{No-Eager} (green, hidden) and \emph{Blocking Eager} (orange, hidden) because the input script features a command in \pur or \npu relatively early.
This command requires an \ttt{agg}regator, whose output is of width 1, and beyond which non-\ttt{split} configurations are sequential (and see no speedup).
% Conversely, all three lines exist when the width remains above 1 for the full program.
% needing a \ttt{split} to regain width. 
Finally, Tab.~\ref{tab:eval} shows that \sys's transformation time is negligible, and its COST~\cite{mcsherryscalability} is 2. %  for all benchmarks.
% Filter and Bigrams-opt, not in Fig.~\ref{fig:microbenchmarks}, achieve speedups of 1.5--2.5$\times$ and 2--30$\times$.
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

@@

\heading{Results}
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for 31 pipelines, with \ttt{width=}16 and 10GB inputs.
It does not include 3 pipelines that use \ttt{head} fairly early thereby finishing execution in under $0.1$ seconds.
We refer to each pipeline using its x-axis index in Fig.~\ref{fig:unix50-individual}.
% The script index refers to the challenge level, in both the plots and the discussion.
% \kk{The above is not exactly true since we sorted them. If someone goes to take a look at the solution source they will be confused.}
Average speedup is \todo{$6.02\times$}, % median is $6.48\times$, 
  and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

\heading{Take-aways} \sys accelerates unmodified pipelines found in the wild;
  small tweaks can yield further improvements, showing that \sys-awareness and scripting expertise can improve results.
Furthermore, \sys does not significantly decelerate non-parallelizable scripts.
% \kk{eurosys: we cant say it doesnt decelarate since it does slow down some of them. If we dont like this sentence we can also delete it.}
% non-trivial computations, even when parallelism is impossible.

@@

\heading{Results}
The complete pipeline executes in 44m2s for five years (82GB) of data.
\sys with \ttt{width=}16 leads to 2.52$\times$ speedup, with different phases seeing different benefits:
  2.04$\times$ (vs. 33m58s) for all the pre-processing and 
  12.31$\times$ speedup (vs. 10m4s) for computing the max.
